%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Freelance Fullstack Developer} % Job title
    {\href{https://www.wonderideas.ch/}{WonderIdeas}} % Organization
    {Agno, Switzerland} % Location
    {Jan 2024 - May 2024} % Date(s)
    {
    \begin{cvitems}
        \item{Build a sales tracker system 
        for the digital transformation of a business. 
        Structured as a 2 tier containerized platform 
        using Django and Vuejs.}
    \end{cvitems}
    }
  
%---------------------------------------------------------
  \cventry
    {Teaching Assistant} % Job title
    {\href{https://www.usi.ch/en}{%
    USI Università della Svizzera italiana}} % Organization
    {Lugano, Switzerland} % Location
    {Feb 2024 - Jun 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Supported \( +150 \) students through lab sessions.
        Presentation and correction of assignment topics.
        \( 15 \) weekly hours during the last semester. }
      \item {\href{https://search.usi.ch/it/corsi/35268192/software-atelier-4-software-engineering-project}{%
      Software Engineering course}: 
      project requirements, 
      fullstack development with Spring Boot and Vue, 
      DevOps practices and docker.}
      \item {\href{https://search.usi.ch/it/corsi/35268184/data-management}{%
      Data Management course}: 
      relational databases, 
      transaction query processing, 
      SQL and NoSQL, 
      Apache Spark for distributed data computation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cloud Engineer} % Job title
    {\href{https://www.claranet.com}{Claranet}} % Organization
    {Lugano, Switzerland} % Location
    {Sep 2023 - Dec 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed cloud assessment challenges with boto3 and AWS 
      Lambda, API Gateway, S3, IAM and Cloud9 services 
      for an internal platform.}
      \item {Provisioning infrastructure on demand 
      with Terraform and Cloudformation IaC tools
      for the assessment routines managed with Python.}
        % \item {Worked on meta study related to analyzing climate papers from Web Of Science, and NSF.}
        % \item {Built a web scraper in nightmare.js to scrape data from Web of Science (WOS), a research paper index, and also collected data from NSF grant database}
        % \item {Used dplyer and R to clean and remove duplicates from WOS along with Postgres to finalized the cleaned data}
        %  \item {Carnegie Classification was used to rank publications from each institution along with the associated journal.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Undergraduate Student Researcher} % Job title
    {
    \href{https://www.si.usi.ch/people}{USI Software Institute}, \href{https://luce.si.usi.ch/team/}{LuCE Research Lab}} % Organization
    {Lugano, Switzerland} % Location
    {Jul 2022 - Aug 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Created backend with FastAPI to convert Python programs' ASTs to
      an expression-based notional machine retaining equivalent graph structure.}
      \item{Purpose: help \( +100 \) new 1st year students 
      understand programming language expressions 
      using the visualization of their abstract syntax trees.%
      }
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\href{https://www.idea-on-line.it/}{%
    Idea Soc. Coop.}} % Organization
    {Ancona, Italy} % Location
    {Feb 2020 - Jul 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {\href{https://www.idea-on-line.it/progetti/boset/}{%
      Blood bag logger}: 
      developed the serial communication procedure from the logger 
      to the docking station sqlite database. 
      Built an embedded local web app for its data visualization
      in Python with Flask and SQLAlchemy to display monitoring information 
      with charts using d3.js.}
      % \item {\href{https://www.idea-on-line.it/progetti/dispositivo-multisensore/}{%
      % Environmental sensor}: 
      % sketched a custom micropython firmware connected to AWS saving data into sqlite database with Alexa skill integration.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  % \cventry
  %   {ICT Technician} % Job title
  %   {BitService Santoni} % Organization
  %   {Ancona, Italy} % Location
  %   {May 2019 - May 2019} % Date(s)
  %   {
  %   \begin{cvitems}
  %       \item{Performing assembling, and maintenance 
  %       of office computers for enterprises.
  %       Setup of both hardware and software of custom pc builds.}
  %   \end{cvitems}
  %   }
  %   \vspace{-0.3cm}

\end{cventries}
